Verifying Demonstrations

### 2018-10-31 paper/intro.tex
intro framing from related work comment

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}

>>>>

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties. \sonja{add and rephrase: 
In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.  }
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}
